---
title: "iteration_and_listcols"
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
set.seed(1)
```

## Lists

You can put anything in a list

```{r}
l= list(
vec_numeric= 5:8,
vec_logical= c(TRUE, TRUE, FALSE, TRUE, FALSE, FALSE),
mat= matrix(1:8, nrow=2, ncol=4),
summary=summary(rnorm(100))
)
```

```{r}
l
l$vec_numeric
l[[1]]
mean(l[[ "vec_numeric"]])
```

## 'for' loop

Create a new list.

```{r}
list_norm=
  list(
    a=rnorm(20, mean=3, sd=1),
    b=rnorm(20, mean=5, sd=1),
    c=rnorm(20, mean=10, sd=0.2),
    d=rnorm(20, mean=-3, sd=1)
    
  )
```

```{r}
list_norm
```

Pause and get my old junction

```{r}
mean_and_sd= function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x)< 3) {
    stop("Input must have at least three numbers")
  }
     
 mean_x=mean(x)
 sd_x=sd(x)
 
 tibble(
   mean=mean_x,
   sd= sd_x
 )

}
```
I can apply that function each list element
```{r}
mean_and_sd(list_norm[[1]])
mean_and_sd(list_norm[[2]])
mean_and_sd(list_norm[[3]])
mean_and_sd(list_norm[[4]])

```
Let's use a for loop

```{r}
output= vector("list", length=4)

for (i in 1:4) {

output[[1]]=mean_and_sd(list_norm[[i]])
}
```

## Let's try map!

```{r}
output= 
map(list_norm, mean_and_sd)
```
What if you want a different function?

```{r}
output= map(list_norm, median)
```

```{r}
output= map_dbl(list_norm, median, .id="input")
```

```{r}
output= map_df(list_norm, mean_and_sd, .id="input")
```

## List Columns

```{r}
listcol_df=
  tibble(
    name=c("a", "b", "c", "d"),
    samp= list_norm
  )
```

```{r}
listcol_df %>% pull(name)
listcol_df %>% pull(samp)

listcol_df %>% 
  filter(name== "a")
```

Let's try some operations

```{r}
mean_and_sd(listcol_df$samp[[1]])
mean_and_sd(listcol_df$samp[[2]])
```
Can I just ....map?

```{r}
map(listcol_df$samp, mean_and_sd)
```
So ..... an I add a list column??

```{r}
listcol_df=
listcol_df %>% 
  mutate(summary = map(samp, mean_and_sd),
         medians = map_dbl (samp, median))
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

Get our list columns..

```{r}
weather_nest=
  weather_df %>% 
  nest(data= date:tmin)
```

```{r}
weather_nest %>% pull(name)
weather_nest %>% pull(data)

weather_nest$data[[3]]
```
Suppose I want to regress `tmax` on `tmin` for each station

This works

```{r}
lm(tmax ~ tmin, data=weather_nest$data[[1]])
```

Let's write a function 

```{r}
weather_lm= function (df){
  
  lm(tmax ~ tmin, data= df )
}

output= vector("list", 3)

for (i in 1:3) {
  
  output[[i]]=weather_lm(weather_nest$data[[i]])
}
```

What about a map....?

```{r}
map(weather_nest$data, weather_lm) 
```

What about map in a list column!?!

```{r}
weather_nest=
weather_nest %>% 
  mutate(models= map(data, weather_lm))

weather_nest$models
```

