---
title: "writing_functions"
output: html_document
---

```{r}
library(tidyverse)
library(rvest)
```

## Do something simple

```{r}
x_vec= rnorm(30, mean=5, sd=3)

(x_vec-mean(x_vec))/sd(x_vec)

```

I want a function to compute z-scores

```{r}

z_scores= function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
    
  z=(x-mean(x))/ sd(x)
  
  return (z)
  
z_scores(x_vec)
}
```

Try my function on some other things. THese should give errors.

```{r, error=TRUE}
z_scores(3)

z_scores("my name is Jeff")

z_scores (mtcars)

z_scores(c(TRUE, TRUE, FALSE, TRUE))
```

## Multiple Outputs

```{r}


mean_and_sd= function(x) {
  
  if (!is.numeric(x)) {
    stop("Input must be numeric")
  }
  
  if (length(x)< 3) {
    stop("Input must have at least three numbers")
  }
     
 mean_x=mean(x)
 sd_x=sd(x)
 
 tibble(
   mean=mean_x,
   sd= sd_x
 )

}
```

Check that the function works


```{r}
x_vec=rnorm (1000)
mean_and_sd(x_vec)
```

## Multiple Inputs

I'd like to do this with a function.

```{r}

sim_data= 
  tibble(
    x=rnorm(n=100, mean=4, sd=3)
  )
sim_data %>% 
  summarize(
    mean=mean(x),
    sd=sd(x)
  )
```

```{r}
sim_mean_sd= function (samp_size, mu = 3, sigma = 4){

  sim_data= 
    tibble(
     x=rnorm(n=samp_size, mean=mu, sd=sigma)
  )
  
sim_data %>% 
  summarize(
    mean=mean(x),
    sd=sd(x)
  )
}

sim_mean_sd(samp_size=100,mu=6, sigma= 3)
sim_mean_sd(mu=6, samp_size= 100, sigma=3)

sim_mean_sd(samp_size=100)
```

## Let's review Napoleon Dynamite
```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)

read_page_reviews <- function(url) {
  
  html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim()
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}
```
What about the next page of reviews....

Let's turn that code into a function

```{r}

read_page_reviews=function(url){
html = read_html(url)

review_titles = 
  html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
   html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
reviews
} 
  

```

Let me try my function

```{r}

dynamite_url="https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=2"

read_page_reviews(dynamite_url)
```

Let's read a few pages of reviews

```{r}
dynamite_url_base= "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

dynamite_urls= str_c(dynamite_url_base, 1:50)

 all_reviews=
bind_rows(
read_page_reviews(dynamite_urls[1]),
read_page_reviews(dynamite_urls[2]),
read_page_reviews(dynamite_urls[3]),
read_page_reviews(dynamite_urls[4]),
read_page_reviews(dynamite_urls[5])
) 
```

## Mean scoping example

```{r}
f=function (x) {
  z= x+y
  z
}

x=1
y=2

f(x=y)
```

